Solving an optimization problem employing restraint programming

### 2015-12-13 proj2/doc/article.tex
temp

\subsection{Search Strategy}

>>>>

\subsection{Search Strategy}
 NUM SEI OQ HEI-DE POR AQUI

 \section{Solution Presentation}
 After the labeling phase, the solution is presented in a way that isn't easily legible by users who have no knowledge of the program's implementation. To aid in the observation and interpretation of the solution, the authors created a predicate which converts it to a more understandable format.
